\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}

% Word count functionality
\immediate\write18{texcount -tex -sum -1 \jobname.tex > \jobname.wordcount.tex}
\newcommand\wordcount{\input{\jobname.wordcount.tex}}

\title{Which Economies Are Most Exposed to a Rise in U.S. Long-Term Yields?}
\author{Matteo Pozzi}
\date{\today}

\begin{document}

\maketitle

\noindent\textbf{Word Count:} \wordcount{} / 800 words

\vspace{0.3cm}

\section{Introduction}

Rising U.S. long-term yields create significant spillover effects across global financial markets, with emerging market (EM) economies exhibiting stronger vulnerabilities. This analysis quantitatively examines which economies are most exposed to U.S. yield increases. The UIP condition is used to derive expected changes in the effective exchange rate (EER) of an economy, with those most exposed to the US economy receiving stronger effects. The analysis is carried out accounting for the relevance of exchange rate risk based on current/financial account imbalances. A linear model is tested against the theory and optimized for reliability. In the end, we propose a short ML alternative to compare performance.

The idea is not to analyze the impact on a single unique variable (inflation or capital flow) but consider the extent to which 

\section{Theoretical Framework}
The log-form Uncovered Interest Parity condition states
\begin{equation}
USY_t \approx i_t^* + e_t - \mathbb{E}(e_t+1)
\end{equation}
where
\begin{itemize}
\item $USY_t$ represents some \textbf{net} US long term yield 
\item $i_t^*$ is the relevant foreign country's counterpart
\item $e_t$ represents effective USD premium to acquire 1 unit of foreign currency in period $t$
\end{itemize}
For a simple \textit{ceteris paribus} analysis let's ignore sovereign default risk and denomination risk, assumed constant across the pre- and post- shock periods.
Approximate in logs


We can estimate the expected future exchange rate, combine that with the estimated inflation pass-through

\subsection{Capital Flow Channel}
We may posit a relationship between U.S. yields and EM capital flows such as:
\begin{equation}
\Delta CF_{i,t} = \alpha + \beta_1 \Delta USY_{t} + \beta_2 VIX_t + \beta_3 X_{i,t} + \epsilon_{i,t}
\end{equation}

where $\Delta CF_{i,t}$ represents capital flow changes to country $i$, $\Delta USY_t$ is the change in U.S. 10-year yields, $VIX_t$ captures global risk appetite, and $X_{i,t}$ includes country-specific fundamentals.
This may evolve in the future but we do not have such data. However, we can imagine capital flows to follow expected changes in the exchange rates to follow arbitrage opportunities. ???

\subsection{Exchange Rate Pass-through}
Currency depreciation following yield increases affects domestic conditions via:
\begin{equation}
\pi_{i,t+1} = \gamma_0 + \gamma_1 \pi_{i,t} + \gamma_2 \Delta e_{i,t} + \gamma_3 \Delta USY_t + u_{i,t}
\end{equation}

where $\pi_{i,t}$ is inflation, $\Delta e_{i,t}$ represents exchange rate depreciation, establishing the link between U.S. monetary conditions and domestic price stability.

\section{Vulnerability Metrics}

\subsection{Financial Vulnerability Index}
A composite vulnerability score can be constructed as:
\begin{equation}
V_i = w_1 \cdot FD_i + w_2 \cdot CA_i + w_3 \cdot RES_i + w_4 \cdot DEBT_i
\end{equation}

where:
\begin{itemize}
\item $FD_i$ = Foreign debt-to-GDP ratio
\item $CA_i$ = Current account deficit-to-GDP ratio  
\item $RES_i$ = Reserves-to-short-term debt ratio (inverted)
\item $DEBT_i$ = USD-denominated debt share
\end{itemize}

\subsection{Interest Rate Sensitivity}
The elasticity of domestic borrowing costs to U.S. yields:
\begin{equation}
\frac{\partial r_{i,t}}{\partial USY_t} = \delta_0 + \delta_1 \cdot RATING_i + \delta_2 \cdot LIQUID_i
\end{equation}

Higher sensitivity indicates greater exposure to U.S. monetary tightening.

\section{Empirical Analysis}

\subsection{Most Vulnerable Economies}

Based on quantitative assessment using 2023 data:

\textbf{High Exposure Tier:}
\begin{itemize}
\item \textbf{Turkey}: External debt 55\% of GDP, current account deficit 4.5\% of GDP, significant USD borrowing
\item \textbf{Argentina}: Debt sustainability concerns, limited reserves, high inflation pass-through
\item \textbf{South Africa}: Twin deficits, reliance on portfolio flows, commodity dependence
\end{itemize}

\textbf{Medium-High Exposure:}
\begin{itemize}
\item \textbf{Indonesia}: Current account sensitivity, significant foreign ownership of government bonds
\item \textbf{Brazil}: Large domestic bond market with foreign participation, currency volatility
\end{itemize}

\subsection{Quantitative Evidence}

Historical analysis of the 2013 "taper tantrum" and 2022 Fed tightening cycle reveals:

\begin{equation}
\beta_{sensitivity} = \frac{\Delta Spread_{i}}{\Delta USY} \approx 1.2-2.5 \text{ for high-exposure EMs}
\end{equation}

This indicates that a 100bp increase in U.S. 10-year yields typically translates to 120-250bp widening in EM sovereign spreads for the most vulnerable economies.

\section{Policy Implications}

Countries can mitigate exposure through:
\begin{itemize}
\item Building foreign exchange reserves: Target ratio $\geq 100\%$ of short-term external debt
\item Developing local currency bond markets to reduce USD dependency
\item Maintaining current account surpluses or manageable deficits ($<3\%$ of GDP)
\item Implementing flexible exchange rate regimes with credible inflation targeting
\end{itemize}

\section{Conclusion}

Economies with high external financing needs, significant USD-denominated debt, and weak fundamentals face the greatest exposure to rising U.S. yields. Turkey, Argentina, and South Africa emerge as particularly vulnerable, while countries with stronger external positions and deeper local markets demonstrate greater resilience. Policymakers should prioritize building buffers and reducing structural vulnerabilities before the next U.S. tightening cycle.

\end{document}